---
title: "TidyTuesday(11/02/2020)"
author: "Matt Leonard"
date: "11/2/2020"
output: html_document
---

```{r}
library(tidytuesdayR)
library(tidyverse)
library(scales)
library(lubridate)
library(zoo)
```


```{r}
print(tuesdata) <- tidytuesdayR::tt_load(2020, week = 44)
```

```{r}
View(tuesdata)
```

```{r}
wind_turbine <- tuesdata$`wind-turbine`
wind_turbine
```


```{r}
wind_turbine %>% 
  count(project_name)
```

```{r}
wind_turbine %>% 
  count(project_name, turbine_number_in_project)
```

```{r}
wind_turbine %>% 
  count(project_name, turbine_number_in_project) %>% 
  separate(turbine_number_in_project, c("turbine_number", "project_total_turbines"), "/", convert = TRUE) -> projects
projects
```

```{r}
projects %>% 
  filter(project_total_turbines > 100) %>% 
  ggplot(aes(reorder(project_name, project_total_turbines), project_total_turbines))+
  geom_bar(stat = "identity")+
  coord_flip()
```

```{r}
wind_turbine %>% 
  ggplot(aes(turbine_rated_capacity_k_w, rotor_diameter_m))+
  geom_point(aes(color = manufacturer)) 
```

It appears that we have strong relationship between turbine capacity and rotor diameter.

```{r}
wind_turbine %>% 
  ggplot(aes(turbine_rated_capacity_k_w, hub_height_m))+
  geom_point(aes(color = manufacturer)) 
```

```{r}
wind_turbine %>% 
  ggplot(aes(turbine_rated_capacity_k_w, total_project_capacity_mw))+
  geom_point(aes(color = manufacturer)) 
```

```{r}
wind_turbine %>% 
  count(manufacturer, sort = TRUE)
```

```{r}
wind_turbine %>% 
  count(manufacturer, sort = TRUE) %>% 
  head(10) %>% 
  ggplot(aes(reorder(manufacturer, n), n)) +
  geom_bar(stat="identity") +
  coord_flip()
```

```{r}
reg <- lm(turbine_rated_capacity_k_w ~ rotor_diameter_m + hub_height_m + manufacturer + total_project_capacity_mw, data = wind_turbine)
```

```{r}
summary(reg)
```

There are some really interesting results showing up here in the very (read: VERY) basic regression we're doing here. Mybe unsurprisingly, we see that both hub_height_m and rotor_diameter_m are showing up as significant predictors of turbine_rated_capacity_k_w. But there appears to be some wide variation among manufacturers as well.

